MixEth: efficient, trustless coin mixing service for Ethereum

### 2019-04-08 article/main.tex
OASIcs version of paper added

\begin{table}[H]
	\centering
	\begin{tabular}{cccc}    
		\begin{minipage}{5cm}
			\procedure{\textsf{Shuffle($PK,C^{*}$)}}{%
				c\stackrel{\$}{\leftarrow}\mathbb{Z}_{|\mathbb{G}|} \\
				C^{'*} \leftarrow cC^{*} \\
				PK^{'} = \{pk^{'}_{i}|pk^{'}_{i}=c*pk_{i} \forall i \in [1..n]\} \\
				\pcreturn (PK^{'},C^{'*}) }
		\end{minipage}
		&
		\begin{minipage}{5.7cm}
			\procedure{\textsf{UploadShuffle($sk_{A},PK,C^{*}$)}}{%
				\pcreturn \textsf{FormTx}(sk_{A},id_{contract},(PK,C^{*})) }
		\end{minipage}
	\end{tabular}
\end{table}

@@

@@

\begin{appendices}

>>>>

\begin{table}[H]
	\centering
	\begin{tabular}{cccc}    
		\begin{minipage}{8cm}
			\procedure{\textsf{Shuffle($PK,C^{*}$)}}{%
				c\stackrel{\$}{\leftarrow}\mathbb{Z}_{|\mathbb{G}|} \\
				C^{*}_{new} \leftarrow cC^{*} \\
				PK^{'} = \{pk^{'}_{i}|pk^{'}_{i}=c*pk_{i} \forall i \in [1..n]\} \\
				proof_{ChP}\stackrel{\$}{\leftarrow} generateChaumPedersen(G,cG,C^{*},C^{*}_{new})\\
				\pcreturn (PK^{'},C^{*}_{new},proof_{ChP}) }
		\end{minipage}
		&
		\begin{minipage}{5.7cm}
			\procedure{\textsf{UploadShuffle($sk_{A},PK,C^{*},proof_{ChP}$)}}{%
				\pcreturn \textsf{FormTx}(sk_{A},id_{contract},(PK,C^{*},proof_{ChP})) }
		\end{minipage}
	\end{tabular}
\end{table}

@@

\subsection{Minimizing shuffling transactions with trusted execution environments}
One might effectively minimize the number of necessary shuffling rounds to $1$. If a Trusted Execution Environment (TEE), e.g., Intel SGX is used to generate the shuffling transaction, then even a single shuffling transaction would suffice to provide the same level of anonymity as if every participant shuffles the public keys. Any of the participants could upload the TEE-generated shuffling transaction, while the MixEth contract could check that indeed the shuffling transaction was generated by a TEE. Such a shortcut would make our scheme even more practical and efficient, however it would subsume trust in Intel regarding the security and confidentiality of the TEE.

@@

\newpage
\begin{appendices}
